Computing in the Field of Rationals

### 2012-06-22 rational_ext.tex
_

@@

@@

%%%%%%%%%%%%%%%%%%%%
\subsection{Categorical Constructions}

>>>>

\begin{proposition}[Size 0 is uninhabited]. 
\label{prop:no-zero-values}
There are no values {{v:b}} when {{[^b^]=0}}.
\end{proposition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Categorical Structure}

As with {{Pi}}, {{PiEE*}} is a dagger symmetric monoidal category with
two monoidal structures. In this section we establish that it is
``locally compact closed'' in the sense that for non-zero objects,
namely types where {{[^ b ^]=0}}, {{PiEE*}} satisfies the conditions
for compact closed categories.

\begin{proposition}[Locally Compact Closed]
{{PiEE*}} is a locally compact closed category in the sense that for
all non-zero objects {{b}}, we have an inverse object {{1/b}} in the
symmetric monoidal structure of {{(*, 1)}}, with the morphisms:

\begin{enumerate}
\item {{1 <-> 1/b * b}} given by {{eta*}}, called the `unit map'.
\item {{b * 1/b <-> 1}} given by {{swap* (;) eps*}}, called the `counit map'.
\end{enumerate}

The following coherence conditions hold (see 2.1 in
\cite{selinger2007dagger}):

\begin{enumerate}
\item {{uniti (;) (eta* (;) swap(*)id) (;)(swap* (*) id) (;) assocr* (;) (id (*) eps*) (;) swap* (;) unite = id}}
\end{enumerate}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Categorical Constructions}
